SCP Briefing Plots - Combined Intervention

### 2024-07-26 minos/outcomes/ChildPovReduction_rel_abs_together.Rmd
Some different working directories in the combined child pov intervention runs

#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/scp_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
workingDir <- "/home/luke/Documents/MINOS/CPR_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old8_scot/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

>>>>

#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/scp_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/MINOS/CPR_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old8_scot/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```
